Generative LLM oversampling for the class imbalance problem in hate speech detection

### 2023-05-16 paper/paper.tex
change metho and results

%P2: Introduce the need for automated methods of hate speech detection
With these developments and the large amount of content on social media sites, these sites have been increasingly looking to automatic detection methods for hate speech \cite{ullmann}. These methods use Machine Learning (ML) to automatically detect and classify hateful speech, removing some of the work done by moderators, whose primary job is to respond reactively to user reports of hate speech \cite{ullmann}. Chandra et al. \cite{chandra} used a combination of image and text processing and classification algorithms to classify images and text on social media sites Twitter and Gab as antisemitic or not \cite{chandra}. In this paper, we seek a lower cost method that uses only the text component of their dataset to further analyze the presence of hate speech on Twitter and investigate new algorithms for classification.\footnote{Our dataset contains less samples than that of \cite{chandra} because Twitter removed some of the hateful posts before we collected the data.}

@@

\section{Previous work}
%P1: mention big paper that you use
Antisemitism detection, as well as hate speech detection generally, has been the subject of much research. Martins et al. \cite{martins} used ML models to analyze and classify antisemitism in posts on social media sites Gab and 4chan, and González-Pizarro and Zanettou \cite{gonzalez} used large language models (LLMs) to do the same. Chandra et al. \cite{chandra} introduced a new dataset of labeled antisemitic posts, including text and images. These posts were labeled not only for whether or not they are antisemitic, but also their type of antisemitism, with the researchers grouping antisemitic posts into political, economic, religious, and racial antisemitism, and trained models to classify both antisemitic status and type of antisemitism. This Twitter dataset is imbalanced, with the non-antisemitic class far outnumbering the antisemitic class, and with political and racial antisemitism being more common than religious and economic antisemitism.

%P2: introduce previous work on class imbalance problem
Imbalance is a common issue in ML classification problems. The class imbalance problem can severely negatively affect model predictive power, with the less common class (termed the ``minority class'') often being misclassified due to its low prevalence in the dataset relative to the larger class (the ``majority class'') \cite{abdelrahman}. This problem has affected fields as distinct as medicine, fraudulent call detection, and risk management \cite{sun}. Due to the severity with which this problem can limit model performance and its widespread nature, being seen in numerous distinct fields, it has become a focus of researchers as an area of improvement \cite{abdelrahman}, with numerous techniques being created to allay the effects of the problem.

@@

%P5: talk about LLMs and their applications, find whether there is research done with LLMs on class imbalance
While these advances in resampling have been occurring, similar advances have been made in generative LLMs, such as the GPT series of models from OpenAI, which have the ability to generate human-like text \cite{floridi} and have been applied to fields such as patent claim generation \cite{hsiang} and healthcare education \cite{sallam}. These LLMs have been investigated as a method for oversampling text data to account for the class imbalance problem, with relatively consistent success over not using resampling \cite{edwards} \cite{usuga} \cite{shaikh}. That being said, these studies do not compare the method with other, simpler or more traditional resampling methods. Drummond \& Holte \cite{drummond} argue that complex methods of resampling are difficult to justify without marked improvements in performance over simpler methods. This provides motivation, now that the method has shown success in accounting for the class imbalance, for investigating how it compares to existing methods of resampling and under which circumstances it improves relative to those methods.

@@

The dataset is imbalanced. Figure 1 shows the distribution of different classes in the dataset. The first and third charts are for the entire dataset, and the second, containing classifications on types of antisemitism, only contains samples that are antisemitic.\\

\begin{nscenter}
\includegraphics[width=.3\textwidth]{binary\_pie.pdf}
\includegraphics[width=.3\textwidth]{type\_pie.pdf}
\includegraphics[width=.3\textwidth]{type5\_pie.pdf}

@@

%P5: talk about evaluation (mean recall) and methods used (cochran, etc)
For model evaluation, the two main metrics used were the macro-averages of the recall and precision scores across each of the classes the model had to classify for each task. This was used in lieu of accuracy in order to account for the class imbalance in the data. Once the models were evaluated, their answers to the testing samples were converted to a binary matrix with each column representing a model and each row representing a sample. We then used the Cochran's Q-test, an extension of McNemar's test appropriate for the case of comparing multiple algorithms on a single domain, to test for significant difference in the models, then the Dunn test for post-hoc analysis.\footnote{See \cite{boukouvalas}} When testing the resampling methods against each other, the data were turned into another matrix with each column representing a resampling method and each row representing a model trained with that method, with the value in the cell being the mean recall or precision of that model. A Friedman's $\chi^2$ test was then performed with a post-hoc Nemenyi test to analyze the results.

{\parskip=0pt
\section{Results}
Overall, the models trained on the LLM-augmented data showed no improvement on the binary task, but they did show improvement on the 5-class classification and especially the 4-class classification tasks. Tables 1 \& 2 contain information for the binary classification task with each resampling method, as well as the best-performing model performance and mean model performance for each resampling method out of the twelve combinations of each algorithm (Naïve Bayes, SVM, Decision Tree, and Extreme Gradient Boosting) and representation method (BoW, TF-IDF, and frequency), with ``performance'' meaning the mean recall or precision score the model achieved. The best model was the best performing model of all of the models trained with that particular resampling method, not taking into account the performance on other resampling methods. The data used to create Table 1 received a Friedman $\chi^2$ test \emph{p}-value of $2.2 \times 10^{-2}$, while Table 2 received a \emph{p}-value of $1.6 \times 10^{-3}$, allowing a rejection of the null hypothesis with $\alpha=0.05$. After each table, an array is provided with the results of the post-hoc Nemenyi test on the resampling methods, with \emph{p}-values displayed in the array. A higher \emph{p}-value and lighter color means we cannot reject the null hypothesis, while a lower \emph{p}-value and darker color means we can. In these arrays, ``RU'' stands for random undersampling, ``ST'' stands for SMOTE with Tomek links, ``RO'' stands for random oversampling, ``AD'' stands for AdaSyn, ``NO'' stands for no resampling method, and ``LA'' stands for LLM-augmented.}
\begin{nscenter}
{\bf Table 1.} Binary task resampling method recall\\

\begin{tabular}{|l|l|l|}
\hline
Resampling Method & Best score (\% over none) & Mean score (\% over none) \\\hline
None (NO) & 0.667 (0\%) & 0.613 (0\%) \\\hline
Random Undersampling (RU) & 0.689 (3.3\%) & {\bf 0.638 (4.1\%)} \\\hline
SMOTE-Tomek (ST) & 0.668 (0.1\%) & 0.614 (0.2\%) \\\hline
Random Oversampling (RO) & {\bf 0.690 (3.4\%)} & 0.623 (1.6\%) \\\hline
AdaSyn (AD) & 0.661 (-0.9\%) & 0.608 (0.8\%) \\\hline
LLM-Augmented (LA) & 0.679 (1.8\%) & 0.617 (0.7\%) \\\hline
\end{tabular}

\includegraphics[scale=0.6]{binary-recall.pdf}\\
{\bf Figure 2.} Binary recall Nemenyi test results\\
\vspace{\baselineskip}
{\bf Table 2.} Binary task resampling method precision\\

\begin{tabular}{|l|l|l|}
\hline
Resampling Method & Best score (\% over none) & Mean score (\% over none) \\\hline
None (NO) & {\bf 0.734 (0\%)} & {\bf 0.644 (0\%)} \\\hline
Random Undersampling (RU) & 0.666 (-9.3\%) & 0.621 (-3.6\%) \\\hline
SMOTE-Tomek (ST) & 0.670 (-8.7\%) & 0.612 (-5.0\%) \\\hline
Random Oversampling (RO) & 0.674 (-8.2\%) & 0.617 (-4.2\%) \\\hline
AdaSyn (AD) & 0.646 (-12.0\%) & 0.600 (-6.8\%) \\\hline
LLM-Augmented (LA) & 0.668 (-9.0\%) & 0.613 (-4.8\%) \\\hline
\end{tabular}

\includegraphics[scale=0.6]{binary-precision.pdf}\\
{\bf Figure 3.} Binary precision Nemenyi test results
\end{nscenter}
In the binary task, the LLM-augmented models show no performance improvement over the other models. Generally, the resampling methods tend to do better than the models with no resampling on recall, but have worse precision performance, with this pattern being sustained by the models trained on LLM-augmented data.

The results of the 5-class classification task are shown below. The data used to create Table 3 received a Friedman $\chi^2$ test \emph{p}-value of $3.4 \times 10^{-6}$, while Table 4 received a \emph{p}-value of $4.1 \times 10^{-2}$.
\begin{nscenter}
{\bf Table 3.} 5-class task resampling method recall\\

\begin{tabular}{|l|l|l|}
\hline
Resampling Method & Best score (\% above none) & Mean score (\% above none) \\\hline
None (NO) & 0.312 (0\%) & 0.265 (0\%) \\\hline
Random Undersampling (RU) & 0.321 (2.9\%) & 0.265 (0\%) \\\hline
SMOTE-Tomek (ST) & 0.289 (-7.4\%) & 0.271 (2.3\%) \\\hline
Random Oversampling (RO) & 0.369 (18.3\%) & 0.298 (12.5\%) \\\hline
AdaSyn (AD) & 0.316 (1.3\%) & 0.251 (-5.3\%) \\\hline
LLM-Augmented (LA) & {\bf 0.402 (28.8\%)} & {\bf 0.347 (30.9\%)} \\\hline
\end{tabular}

\includegraphics[scale=0.6]{5type-recall.pdf}\\
{\bf Figure 4.} 5-class recall Nemenyi test results\\
\vspace{\baselineskip}
{\bf Table 4.} 5-class task resampling method precision\\

\begin{tabular}{|l|l|l|}
\hline
Resampling Method & Best score (\% above none) & Mean score (\% above none) \\\hline
None (NO) & {\bf 0.524 (0\%)} & {\bf 0.325 (0\%)} \\\hline
Random Undersampling (RU) & 0.274 (-47.7\%) & 0.249 (-23.4\%) \\\hline
SMOTE-Tomek (ST) & 0.295 (-43.7\%) & 0.264 (-18.8\%) \\\hline
Random Oversampling (RO) & 0.319 (-39.1\%) & 0.271 (-16.6\%) \\\hline
AdaSyn (AD) & 0.436 (-16.8\%) & 0.286 (-12.0\%) \\\hline
LLM-Augmented (LA) & 0.302 (-42.4\%) & 0.270 (-16.9\%) \\\hline
\end{tabular}

\includegraphics[scale=0.6]{5type-precision.pdf}\\
{\bf Figure 5.} 5-class precision Nemenyi test results
\end{nscenter}
The results on the 5-type task begin to show the benefits of LLM augmentation. The pattern of no resampling outperforming resampling on precision while the inverse happens on recall remains, but now LLM augmentation improves over no resampling by a far wider margin than any other resampling method, while retaining similar levels of drops in precision to other methods. Now, its gain in mean recall is larger than its loss in mean precision, which is not the case for any other resampling method in the 5-class task, and is only true for random undersampling in the binary task.

The results of the 4-class classification task are shown below. The data used to create Table 5 received a Friedman $\chi^2$ test \emph{p}-value of $5.3 \times 10^{-4}$, while Table 6 received a \emph{p}-value of $4.2 \times 10^{-5}$.
\begin{nscenter}
{\bf Table 5.} 4-class task resampling method recall\\

\begin{tabular}{|l|l|l|}
\hline
Resampling Method & Best score (\% above none) & Mean score (\% above none) \\\hline
None (NO) & 0.337 (0\%) & 0.328 (0\%) \\\hline
Random Undersampling (RU) & 0.414 (22.8\%) & 0.339 (3.4\%) \\\hline
SMOTE-Tomek (ST) & 0.420 (24.6\%) & 0.366 (11.6\%) \\\hline
Random Oversampling (RO) & 0.400 (18.7\%) & 0.358 (9.1\%) \\\hline
AdaSyn (AD) & 0.471 (39.8\%) & 0.322 (-1.8\%) \\\hline
LLM-Augmented (LA) & {\bf 0.509 (51.0\%)} & {\bf 0.433 (32.0\%)} \\\hline
\end{tabular}

\includegraphics[scale=0.6]{4type-recall.pdf}\\
{\bf Figure 6.} 4-class recall Nemenyi test results\\
\vspace{\baselineskip}
{\bf Table 6.} 4-class task resampling method precision\\

\begin{tabular}{|l|l|l|}
\hline
Resampling Method & Best score (\% above none) & Mean score (\% above none) \\\hline
None (NO) & 0.452 (0\%) & 0.372 (0\%) \\\hline
Random Undersampling (RU) & 0.361 (-17.9\%) & 0.323 (-13.2\%) \\\hline
SMOTE-Tomek (ST) & 0.381 (-15.7\%) & 0.347 (-6.7\%) \\\hline
Random Oversampling (RO) & 0.374 (-17.3\%) & 0.351 (-5.6\%) \\\hline
AdaSyn (AD) & 0.378 (-16.4\%) & 0.344 (-7.5\%) \\\hline
LLM-Augmented (LA) & {\bf 0.504 (11.5\%)} & {\bf 0.409 (9.9\%)} \\\hline
\end{tabular}

\includegraphics[scale=0.6]{4type-precision.pdf}\\
{\bf Figure 5.} 4-class precision Nemenyi test results
\end{nscenter}
Now, the pattern of gains on recall and losses on precision continue for all methods except LLM augmentation. LLM-augmented models not only increase the recall by a greater margin than any other method, but also increase the precision of the model on the 4-class task. This makes it the only resampling method in any of the three tasks to receive a higher precision score either on the best model or on mean score than no resampling, on top of widening the margin by which it beats no resampling compared to the 5-class task.

One initial possible explanation for the high performance of the models with LLM-augmented data relative to other models on the 5-class and especially 4-class tasks is that the LLM augmentation provides performance improvements with only one particular class that other resampling methods did poorly on, artificially raising the mean recall even though there was only one class affected significantly. Looking further at the data, however, while some classes were more affected than others, overall, the models trained on LLM-augmented data show improvements in multiple classes. On the 4-type classification task, Tables 7 \& 8 show the mean recall and precision of each method on each particular class, respectively.
\begin{nscenter}
{\bf Table 7.} 4-class task class-wise resampling method recall\\

\begin{tabular}{|l|l|l|l|l|}
\hline
Resampling Method & Political & Economic & Religious & Racial \\\hline
None (NO) & {\bf 0.618} & 0.106 & 0.203 & 0.283 \\\hline
Random Undersampling (RU) & 0.379 & {\bf 0.240} & 0.434 & 0.200  \\\hline
SMOTE-Tomek (ST) & 0.506 & 0.135 & 0.465 & 0.245 \\\hline
Random Oversampling (RO) & 0.487 & 0.163 & 0.442 & 0.230 \\\hline
AdaSyn (AD) & 0.574 & 0.135 & 0.223 & 0.258 \\\hline
LLM-Augmented (LA) & 0.492 & 0.231 & {\bf 0.471} & {\bf 0.405} \\\hline
\end{tabular}

{\bf Table 8.} 4-class task class-wise resampling method precision\\

\begin{tabular}{|l|l|l|l|l|}
\hline
Resampling Method & Political & Economic & Religious & Racial \\\hline
None (NO) & 0.598 & 0.029 & 0.254 & 0.390 \\\hline
Random Undersampling (RU) & 0.601 & 0.024 & 0.205 & 0.362 \\\hline
SMOTE-Tomek (ST) & 0.653 & 0.018 & 0.234 & 0.378 \\\hline
Random Oversampling (RO) & {\bf 0.661} & 0.015 & 0.227 & 0.392 \\\hline
AdaSyn (AD) & 0.602 & 0.017 & 0.243 & 0.390 \\\hline
LLM-Augmented (LA) & 0.577 &{\bf  0.111} & {\bf 0.367} & {\bf 0.431} \\\hline
\end{tabular}
\end{nscenter}
In precision and recall, the model is outperformed in political antisemitism (the largest class), and in recall it is slightly outperformed by random undersampling in economic antisemitism, but it outperforms the other models in religious and racial antisemitism on recall and in all classes other than political in precision.

>>>>

%P2: Introduce the need for automated methods of hate speech detection
With these developments and the large amount of content on social media sites, these sites have been increasingly looking to automatic detection methods for hate speech \cite{ullmann}. These methods use Machine Learning (ML) to automatically detect and classify hateful speech, removing some of the work done by moderators, whose primary job is to respond reactively to user reports of hate speech \cite{ullmann}. \cite{chandra} used a combination of image and text processing and classification algorithms to classify images and text on social media sites Twitter and Gab as antisemitic or not \cite{chandra}. In this paper, we seek a lower cost method that uses only the text component of their dataset to further analyze the presence of hate speech on Twitter and investigate new algorithms for classification.\footnote{Our dataset contains fewer samples than that of \cite{chandra} because Twitter removed some of the hateful posts before we collected the data.}

@@

\section{Previous work}
%P1: mention big paper that you use
Antisemitism detection, as well as hate speech detection generally, has been the subject of much research. \cite{martins} used ML models to analyze and classify antisemitism in posts on social media sites Gab and 4chan, and \cite{gonzalez} used large language models (LLMs) to do the same. \cite{chandra} introduced a new dataset of labeled antisemitic posts, including text and images. These posts were labeled not only for whether or not they are antisemitic, but also their type of antisemitism, with the researchers grouping antisemitic posts into political, economic, religious, and racial antisemitism, and trained models to classify both antisemitic status and type of antisemitism. This Twitter dataset is imbalanced, with the non-antisemitic class far outnumbering the antisemitic class, and with political and racial antisemitism being more common than religious and economic antisemitism.

%P2: introduce previous work on class imbalance problem
Imbalance is a common issue in ML classification problems. The class imbalance problem can severely negatively affect model predictive power, with the less common class (termed the ``minority class'') often being misclassified due to its low prevalence in the dataset relative to the larger class (the ``majority class'') \cite{abdelrahman}. In multiclass classification, the classes with fewer samples will similarly perform worse to those with more samples. This problem has affected fields as distinct as medicine, fraudulent call detection, and risk management \cite{sun}. Due to the severity with which this problem can limit model performance and its widespread nature, being seen in numerous distinct fields, it has become a focus of researchers as an area of improvement \cite{abdelrahman}, with numerous techniques being created to allay the effects of the problem.

@@

%P5: talk about LLMs and their applications, find whether there is research done with LLMs on class imbalance
While these advances in resampling have been occurring, similar advances have been made in generative LLMs, such as the GPT series of models from OpenAI, which have the ability to generate human-like text \cite{floridi} and have been applied to fields such as patent claim generation \cite{hsiang} and healthcare education \cite{sallam}. These LLMs have been investigated as a method for oversampling text data to account for the class imbalance problem, with relatively consistent success over not using resampling \cite{edwards} \cite{usuga} \cite{shaikh}. That being said, these studies do not compare the method with other, simpler or more traditional resampling methods.  \cite{drummond} argues that complex methods of resampling are difficult to justify without marked improvements in performance over simpler methods. This provides motivation, now that the method has shown success in accounting for the class imbalance, for investigating how it compares to existing methods of resampling and under which circumstances it improves relative to those methods.

@@

The dataset is imbalanced. Figure 1 shows the distribution of different classes in the dataset. The first and second charts are for the entire dataset, and the third, containing classifications on types of antisemitism, only contains samples that are antisemitic.\\

\begin{nscenter}
\includegraphics[width=.3\textwidth]{binary\_pie.pdf}
\includegraphics[width=.3\textwidth]{type5\_pie.pdf}
\includegraphics[width=.3\textwidth]{type\_pie.pdf}

@@

%P5: talk about evaluation (mean recall) and methods used (cochran, etc)
For model evaluation, the three main metrics used were the macro-averages of the recall, precision, and $F_1$ scores across each of the classes the model had to classify for each task. These were used in lieu of accuracy in order to account for the class imbalance in the data. Once the models were evaluated, their answers to the testing samples were converted to a binary matrix with each column representing a model and each row representing a sample. We then used the Cochran's Q-test, an extension of McNemar's test appropriate for the case of comparing multiple algorithms on a single domain, to test for significant difference in the models, then the Dunn test for post-hoc analysis.\footnote{See \cite{boukouvalas}} When testing the resampling methods against each other, the data were turned into another matrix with each column representing a resampling method and each row representing a model trained with that method, with the value in the cell being the mean recall, precision, or $F_1$ score of that model. A Friedman's $\chi^2$ test was then performed with a post-hoc Nemenyi test to analyze the results.

{\parskip=0pt
\section{Results}
Overall, the models trained on the LLM-augmented data showed no improvement on the binary task, but they did show improvement on the 5-class classification and especially the 4-class classification tasks. Tables 1 contains information for the binary classification task with each resampling method, as well as the mean model performance for each resampling method out of the twelve combinations of each algorithm (Naïve Bayes, SVM, Decision Tree, and Extreme Gradient Boosting) and representation method (BoW, TF-IDF, and frequency), with ``performance'' meaning the mean recall, precision, or $F_1$ score the model achieved. The data used to create the $F_1$ column of Table 1 received a Friedman $\chi^2$ test \emph{p}-value of $2.2 \times 10^{-2}$, allowing a rejection of $H_0$ that each method comes from the same distribution with $\alpha=0.05$. After each table, an array is provided with the results of the post-hoc Nemenyi test on the resampling methods for the $F_1$ score, with \emph{p}-values displayed in the array. A higher \emph{p}-value and lighter color means we cannot reject the null hypothesis, while a lower \emph{p}-value and darker color means we can. In these arrays, ``RU'' stands for random undersampling, ``ST'' stands for SMOTE with Tomek links, ``RO'' stands for random oversampling, ``AD'' stands for AdaSyn, ``NO'' stands for no resampling method, and ``LA'' stands for LLM-augmented.}
\begin{nscenter}
{\bf Table 1.} Binary task resampling method performance\\

\begin{tabular}{|l|l|l|l|}
\hline
Resampling Method & Recall (\% over none) & Precision (\% over none) & $F_1$ (\% over none) \\\hline
 None (NO) & 0.613 (0\%) & {\bf 0.644 (0\%)} & 0.627 (0\%) \\\hline
 RandomUnder (RU) & {\bf 0.638 (4.1\%)} & 0.621 (-3.6\%) & {\bf 0.630 (0.5\%)} \\\hline
 SMOTE-Tomek (ST) & 0.614 (0.1\%) & 0.612 (-5.0\%) & 0.613 (-2.2\%) \\\hline
 Random Over (RO) & 0.623 (1.6\%) & 0.617 (-4.2\%) & 0.620 (-1.1\%) \\\hline
 AdaSyn (AD) & 0.608 (-0.8\%) & 0.600 (-6.8\%) & 0.604 (-3.7\%) \\\hline
 LLM-Augmented (LA) & 0.617 (0.6\%) & 0.613 (-4.8\%) & 0.614 (-2.1\%) \\\hline
\end{tabular}

\includegraphics[scale=0.6]{binary-f1.pdf}\\
{\bf Figure 2.} Binary $F_1$ Nemenyi test results\\
\end{nscenter}
In the binary task, the LLM-augmented models show no performance improvement over the other models. Generally, the resampling methods tend to do better than the models with no resampling on recall, but have worse precision performance, with this pattern being sustained by the models trained on LLM-augmented data.

The results of the 5-class classification task are shown below. The data used to create the $F_1$ column of Table 2 received a Friedman $\chi^2$ test \emph{p}-value of $1.6 \times 10^{-3}$.
\begin{nscenter}
{\bf Table 2.} 5-class task resampling method performance\\

\begin{tabular}{|l|l|l|l|}
\hline
Resampling Method & Recall (\% over none) & Precision (\% over none) & $F_1$ (\% over none) \\\hline
 None (NO) & 0.265 (0\%) & {\bf 0.325 (0\%)} & 0.286 (0\%) \\\hline
 RandomUnder (RU) & 0.265 (0\%) & 0.249 (-23.4\%) & 0.256 (-10.4\%) \\\hline
 SMOTE-Tomek (ST) & 0.271 (2.3\%) & 0.264 (-18.8\%) & 0.267 (-6.6\%) \\\hline
 Random Over (RO) & 0.298 (12.4\%) & 0.271 (-16.6\%) & 0.283 (-1.0\%) \\\hline
 AdaSyn (AD) & 0.251 (-5.3\%) & 0.286 (-12.0\%) & 0.264 (-7.7\%) \\\hline
 LLM-Augmented (LA) & {\bf 0.347 (30.9\%)} & 0.270 (-16.9\%) & {\bf 0.303 (5.9\%)} \\\hline
\end{tabular}

\includegraphics[scale=0.6]{5type-f1.pdf}\\
{\bf Figure 3.} 5-class $F_1$ Nemenyi test results\\
\end{nscenter}
The results on the 5-type task begin to show the benefits of LLM augmentation. The pattern of no resampling outperforming resampling on precision while the inverse happens on recall remains, but now LLM augmentation improves over no resampling by a far wider margin than any other resampling method, making its gain in mean recall account for its loss in precision, giving it a higher $F_1$ score than the other methods.

The results of the 4-class classification task are shown below. The data used to create the $F_1$ column of Table 3 received a Friedman $\chi^2$ test \emph{p}-value of $7.1 \times 10^{-5}$.
\begin{nscenter}
{\bf Table 3.} 4-class task resampling method performance\\

\begin{tabular}{|l|l|l|l|}
\hline
Resampling Method & Recall (\% over none) & Precision (\% over none) & $F_1$ (\% over none) \\\hline
 None (NO) & 0.328 (0\%) & 0.372 (0\%) & 0.346 (0\%) \\\hline
 RandomUnder (RU) & 0.339 (3.3\%) & 0.323 (-13.2\%) & 0.330 (-4.6\%) \\\hline
 SMOTE-Tomek (ST) & 0.366 (11.6\%) & 0.347 (-6.7\%) & 0.356 (2.9\%) \\\hline
 Random Over (RO) & 0.358 (9.1\%) & 0.351 (-5.6\%) & 0.354 (2.3\%) \\\hline
 AdaSyn (AD) & 0.322 (-1.8\%) & 0.344 (-7.5\%) & 0.331 (-4.3\%) \\\hline
 LLM-Augmented (LA) & {\bf 0.433 (32.0\%)} & {\bf 0.409 (9.9\%)} & {\bf 0.419 (21.1\%)} \\\hline
\end{tabular}

\includegraphics[scale=0.6]{4type-f1.pdf}\\
{\bf Figure 4.} 4-class $F_1$ Nemenyi test results\\
\end{nscenter}
Now, the pattern of gains on recall and losses on precision continue for all methods except LLM augmentation. LLM-augmented models not only increase the recall by a greater margin than any other method, but also increase the precision of the model on the 4-class task. This makes it the only resampling method in any of the three tasks to receive a higher precision score either on the best model or on mean score than no resampling, on top of widening the margin by which it beats no resampling compared to the 5-class task.

One initial possible explanation for the high performance of the models with LLM-augmented data relative to other models on the 5-class and especially 4-class tasks is that the LLM augmentation provides performance improvements with only one particular class that other resampling methods did poorly on, artificially raising the mean recall even though there was only one class affected significantly. Looking further at the data, however, while some classes were more affected than others, overall, the models trained on LLM-augmented data show improvements in multiple classes. On the 4-type classification task, Table 4 shows the mean $F_1$ of each method on each particular class, respectively.
\begin{nscenter}
{\bf Table 4.} 4-class task class-wise resampling method $F_1$ score\\

\begin{tabular}{|l|l|l|l|l|}
\hline
Resampling Method & Political & Economic & Religious & Racial \\\hline
None (NO) & {\bf 0.597} & 0.059 & 0.233 & 0.315 \\\hline
Random Undersampling (RU) & 0.463 & 0.050 & 0.276 & 0.253 \\\hline
SMOTE-Tomek (ST) & 0.568 & 0.056 & 0.304 & 0.288 \\\hline
Random Oversampling (RO) & 0.558 & 0.038 & 0.294 & 0.280 \\\hline
AdaSyn (AD) & 0.581 & 0.046 & 0.228 & 0.301 \\\hline
LLM-Augmented (LA) & 0.526 & {\bf 0.161} & {\bf 0.403} & {\bf 0.415} \\\hline
\end{tabular}
\end{nscenter}
In $F_1$ score, the model is outperformed in political antisemitism (the largest class), but it outperforms the other models in all other classes.
